---
title: "Task 18"
author: "Haleigh Borich"
date: "11/7/2021"
output:  
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'
---
I chose to look at the stock prices for American Airlines (AAL), T-Mobile (TMUS), and Microsoft Corp (MSFT). My friends chose Kellogg Company (K), AMC Entertainment (AMC), and Walt Disney Co (DIS)

```{r}
library(tidyquant)
library(tidyverse)
library(lubridate)
library(timetk)
library(dygraphs)
```
Setting the Time Frame
```{r}
start <- today() - years(1)
  end <- today()
```

My Picks
```{r}
(AmericanAir <- tq_get("AAl", get = "stock.prices", from = start, to = end))
(Tmobile <- tq_get("TMUS", get = "stock.prices", from = start, to = end))
(Mircosoft <- tq_get("MSFT", get = "stock.prices", from = start, to = end))
```
Friend's Picks
```{r}
(Kellogg <- tq_get("K", get = "stock.prices", from = start, to = end))
(AMC <- tq_get("AMC", get = "stock.prices",from = start, to = end))
(Disney <- tq_get("DIS", get = "stock.prices", from = start, to = end))
```
Combining them all together
```{r}
total <- tq_get(c("AAL", "TMUS", "MSFT", "K", "AMC", "DIS"), get = "stock.prices", from = start, to = end)

head(total)
tail(total)
```

```{r}
total_xts <- total %>%
  select(symbol, date, adjusted) %>%
  pivot_wider(names_from = symbol, values_from = adjusted) %>%
  tk_xts(date_var = date)

dygraph(total_xts)
```
After looking at this graph, it is clear the Microsoft has the highest stock prices out of the chosen six to examine. Because of that, I will be just looking at the Microsoft stocks to see which stock is helping them be so successful.
```{r}
total %>%
  filter(symbol == "MSFT") %>%
  ggplot(aes(x = date, y = adjusted)) +
  geom_candlestick(aes(open = open, high = high, low = low, close = close)) +
  labs(title = "Candlestick Chart", 
       y = "Closing Price", x = "") + 
  coord_x_date(xlim = c(start, end)) +
  theme_tq()
```
With the candlestick chart, I can see that Microsoft has had a steady growth since June 2021 with a slight dip in September 2021. When Microsoft hit their slight dip, it was mainly because their closing price was lower than the opening price. 
