---
title: "Case Study 6 Markdown"
author: "Haleigh Borich"
date: "10/4/2021"
output: 
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'
---

Load in Libraries
```{r}
library(tidyverse)
library(RColorBrewer)
```
Load in data
```{r}
head(diamonds)
str(diamonds)
```
1. Make visualizations to give the distribution of each of the x, y, and z variables in the diamonds data set.
Graph for X
```{r}
ggplot(diamonds, aes(x = x)) +
  stat_bin(breaks = seq(0, 10.74, .01), alpha = .9) +
  theme_bw()
```
Graph for Y
```{r}
ggplot(diamonds, aes(x = y)) +
  stat_bin(breaks = seq(3, 10, .01), alpha = .9) +
  theme_bw()
```
Graph for Z
```{r}
ggplot(diamonds, aes(x = z)) +
  stat_bin(breaks = seq(2, 6.5, .01), alpha = .9) +
  theme_bw()
```
2. Explore the distribution of price. Is there anything unusual or surprising?
```{r}
ggplot(diamonds, aes(x = price)) +
  stat_bin(breaks = seq(326, 18823, 50)) +
  theme_bw()
```
After looking at this graph I can see there is a blank space somewhere between 0 and 2,500.
Closer Look Graph
```{r}
closerlook <- diamonds %>%
  filter(price < 2500) 

ggplot(closerlook, aes(x = price)) +
  stat_bin(breaks = seq(326, 2500, 10)) +
  theme_bw()
```
From this, I can tell there is no diamonds being sold in between the range 14,000 through 1,500. There seems to be a certain threshold.

3. Can you determine what variable in the diamonds dataset is most important for predicting the price of a diamond? How is that variable correlated with cut? Why does the combination of those two relationships lead to lower quality diamonds being more expensive?
```{r}
ggplot(diamonds, aes(x = price, color = cut,)) +
  geom_density() +
  theme_bw()
```

```{r}
ggplot(diamonds, aes(x = price, fill = cut)) +
  stat_bin(breaks = seq(0, 20000, 500)) +
  facet_wrap(~ cut, ncol = 3, scales = "free") +
  theme_bw()
```

```{r}
diamonds %>%
  mutate(color = fct_rev(color)) 

ggplot(diamonds, aes(x = color, y = price, fill = color)) +
  geom_boxplot() +
  theme_bw()
```
There is a negative correlation between color and price. 
```{r}
ggplot(diamonds, aes(x = clarity, y = price, fill = clarity)) +
  geom_boxplot() +
  theme_bw()
```
There is also a negative relationship with clairty and price
4. Make a visualization of carat partitioned by price.
Create a New column
```{r}
new_diamonds <- diamonds %>%
  mutate(pricegroup = 
           case_when(
             price >= 0 & price <= 2000 ~ "1 - 2000",

price >= 2001 & price <= 4000 ~ "2001 - 4000",
             price >= 4001 & price <= 6000 ~ "4001 - 6000",
             price >= 6001 & price <= 8000 ~ "6001 - 8000",
             price >= 8001 & price <= 10000 ~ "8001 - 10000",
             price >= 10001 & price <= 12000 ~ "10001 - 12000",
             price >= 12001 & price <= 14000 ~ "12001 - 14000",
             price >= 14001 & price <= 16000 ~ "14001 - 16000",
             price >= 16001 & price <= 18000 ~ "16001 - 18000",
             price >= 18001 & price <= 20000 ~ "18001 - 20000"),
         pricegroup = fct_relevel(pricegroup,
                                  "1 - 2000", "2001 - 4000", "4001 - 6000", "6001 - 8000", "8001 - 10000", "10001 - 12000", "14001 - 16000", "18001 - 20000"))

```
Graph
```{r}
ggplot(new_diamonds, aes(x = pricegroup, y = carat, fill = pricegroup)) +
  geom_boxplot() +
  coord_flip() +
  scale_fill_brewer(palette = "Paired") +
  theme_bw()
```
5. How does the price distribution of very large diamonds compare to small diamonds? Does the data agree with your expectations?
```{r}
diamonds %>%
  filter(between(carat, 0, 2.5)) %>%
  mutate(carat = cut_width(carat, 1))

ggplot(diamonds, aes(x = price)) +
  stat_bin(breaks = seq(0, 19000, 200)) +
  theme_bw()

```
I am a little surprised by the lack of difference of the distribution as price goes up. 
6. Visualize a combined distribution of cut, carat, and price.
```{r}
diamonds %>%
  filter(between(carat, 0, 2.5)) %>%
  mutate(carat = cut_width(carat, 1)) %>%
  ggplot(aes(x = cut, y = price, fill = cut)) +
  geom_boxplot() +
  facet_wrap(~ carat) +
  scale_fill_manual(values = c("#B81918", "#D45625", "#EAB521", "#E4D51F", "#A9D222")) +
  theme_bw()
```


