---
title: "Case Study 5"
author: "Haleigh Borich"
date: "9/27/2021"
output: 
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'
---

Load in the Libraries
```{r}
library(tidyverse)
library(downloader)
library(readxl)
```
Read in Data
```{r}
GunData <- tempfile()
download("https://raw.githubusercontent.com/fivethirtyeight/guns-data/master/full_data.csv", GunData, mode = "wb")
GunData1 <- read_csv(GunData)
```
Look at the data & structure
```{r}
head(GunData1)
str(GunData1)
```
Filter out the N/A value
```{r}
NewGunData <- GunData1 %>%
  filter(age != "", intent != "")
```
Create a new column named "Age Group"
```{r}
agegroup <- NewGunData %>%
  mutate(agegroup =
           case_when(
             age >= 0 & age <= 14 ~ "under 15.",
             age >= 15 & age <= 34 ~ "15 - 34",
             age >= 35 & age <= 64 ~ "35 - 64",
             age >= 65 ~ "65+"), 
         agegroup = fct_relevel(agegroup,
                                "under 15.", "15 - 34", "35 - 64", "65+")
         )
```
Create a Graph for the data
```{r}
ggplot(data = agegroup, mapping = aes(x = agegroup, fill = sex)) +
  geom_bar() +
  facet_wrap(~ intent, nrow = 2, scales = "free") +
  scale_fill_manual(values = c("#D784B4", "#5A84D3")) +
  theme_bw() +
  labs(title = "Different types of Gun Deaths through Age Groups")
```
The second visualization does not require preparation like the first graphic.
Create a Graph
```{r}
ggplot(data = NewGunData, mapping = aes(x = age, fill = intent)) +
  geom_density(alpha = .6, position = "fill") +
  facet_wrap(~ sex) +
  scale_fill_manual(values = c("#8CDBAA","#FFA727","#B2C2F8","#F9A5E4")) +
  labs(title = "Gun Deaths through the Genders")
```
Create a New Column named "Seasons"
```{r}
seasons <- NewGunData %>%
  mutate(month = as.factor(month))
```
Make the column "Month" an Integer
```{r}
NewGunData$month <- as.integer(NewGunData$month)
```
Create the seasons within the new column
```{r}
seasons <- NewGunData %>%
  mutate(season =
           case_when(
             month >= 3 & month <= 5 ~ "Spring",
             month >= 6 & month <= 8 ~ "Summer",
             month >= 9 & month <= 11 ~ "Fall",
             month >= 1 & month <= 2 ~ "Winter",
             month == 12 ~ "Winter"))
```
Graphic #1
```{r}
ggplot(data = seasons, mapping = aes(x = season, fill = season)) +
  geom_bar() +
  theme_bw()
```
In this graph, I plotted the different seasons and the count of deaths per season. The reason this graph is important is because it shows that season does not make a difference in Gun Deaths.

Graphic #2
```{r}
ggplot(data = seasons, mapping = aes(x = season, fill = season)) +
  geom_bar() +
  facet_wrap(~ intent, nrow = 2, scales = "free") +
  theme_bw()
```
I created this graph because I wanted to see the different types of deaths throughout the seasons. From this we can assume that the season does not have an effect of the type of deaths.
