---
title: "Task8Markdown"
author: "Haleigh Borich"
date: "9/22/2021"
output: 
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'
---
Load in libraries
```{r }
library(tidyverse)
```
I needed to set my working directory so first I found it and then reset it
```{r}
getwd()
#setwd("/Users/haleighborich/DTS 350/borichh/Week5/Task8")
# I marked this part out that way you do not accidentally run it.
```
Load in Data set
```{r}
BSLData <- read_csv("heights.csv")
```
Look at the firs & last 6 rows and structure
```{r}
head(BSLData)
tail(BSLData)
str(BSLData)
```
Create a new column named grade were the grade is specified with a word instead of a number
```{r}
HeightEd <- BSLData %>%
  mutate(grade = 
           case_when(
             ed >= 3 & ed <= 6 ~ "primary",
             ed >= 7 & ed <=11 ~ "secondary",
             ed == 12 ~ "highschoolgrad",
             ed >= 13 & ed <=15 ~ "associate",
             ed == 16 ~ "bachelors",
             ed >= 17 & ed <= 18 ~ "masterdoctorate"
           ))
```
Create a grpahic for the relationship between Race & Education
```{r}
HeightEd %>%
  mutate(grade = as.factor(fct_reorder(grade, earn))) %>%
  ggplot(aes(x = race, y = earn, fill = race)) +
  geom_col(position = "dodge") +
  facet_wrap(~ grade, nrow = 1) +
  labs(x = "Race", 
       y = "Earnings",
       title = "Relationship between Race & Education",
       subtitle = "We can assume that the more you earn, the better education
       you recieved.") +
  theme_bw()
```
Create a graphic for the relationship between Sex/Gender & Educaiton
```{r}
HeightEd %>%
  mutate(grade = as.factor(fct_reorder(grade, earn))) %>%
  ggplot(aes(x = sex, y = earn, fill = sex)) +
  geom_col(position = "dodge") +
  facet_wrap(~ grade, nrow = 1) +
  labs(x = "Sex/Gender", 
       y = "Earnings",
       title = "Relationship between Sex & Education",
       subtitle = "We can assume that earnings increase due to the education recieved.")
  theme_bw()
```
Create a graphic to compare earnings through Race & Gender
```{r}
HeightEd %>%
  mutate(race = fct_lump(race)) %>%
  ggplot(aes(x = sex, y = earn, fill = sex)) +
  geom_col(position = "dodge") +
  facet_wrap(~ race, nrow = 1) +
  labs(x = "Sex/Gender",
       y = "Earnings",
       title = "Comparing Earnings through Race & Gender",
       subtitle = "Other consists of African Americans, Hispanics, and the Original Other",
       captions = "While making this graph, I learned the importance of lumping data together.
       I had orignally created a grpah showing the difference between all of the races, but 
       I thought it would be more useful to show how White people have a severe advantage when
       it comes to salary. From this graph, we can see that White people have close to triple 
       the amount of earning than any other race.") +
  theme_bw()
```


