---
title: "Case Study 4"
author: "Haleigh Borich"
date: "9/20/2021"
output:
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'

---

Load Data 
```{r}
library(nycflights13)
library(tidyverse)
library(ggrepel)
```
Look at Flights Data & Structure
```{r}
?flights
str(flights)
head(flights)
```
1. f I am leaving before noon, which two airlines do you recommend at each airport (JFK, LGA, EWR) that will havethe lowest delay time at the 75th percentile?
```{r}
LowDelay <- ggplot(data = flights, mapping = aes(x = carrier, y = arr_delay, color = carrier, size = arr_delay)) +
  geom_point() +
  labs(x = "Airline Carrier",
       y = "Arrival Delay",
       title = "If I am leaving before noon, which two airlines 
       do you recommend at each airport (JFK, LGA, EWR) that 
       will havet he lowest delay time at the 75th percentile?",
       subtitle = "SkyWest Airlines Inc. is the best carrier ",
       caption = "We can see that SkyWest Airlines Inc. is the 
       best for a flight because it has the lowest Arrival Delays")
LowDelay
```
From this graph, I was able to tell that SkyWest Arilines Inc. was the best carrier to go through because it had the least amount of points

Which destination airport is the worst airport for 
arrival time?
```{r}
WorstAirline <- ggplot(data = flights, mapping = aes(x = origin, y = arr_delay, color = origin, size = arr_delay)) +
  geom_point() +
  labs(x = "Origin Airport", 
       y = "Arrival Delay",
       title = "Which destination airport is the worst airport for arrival time?",
       subtitle = "JFK is the worst location to fly out of",
       caption = "We know this because it has a high density of points") +
  theme_bw()
WorstAirline
```
The worst airline is JFK because, and I was able to figure that out because it has the most points laying towards the top of the graph, meaning it has the most late arrivals. 
