---
title: "Case Study 4"
author: "Haleigh Borich"
date: "9/20/2021"
output:
  html_document:
    theme: united
    keep_md: True
    code_folding: 'hide'

---

Load Data 
```{r}
library(nycflights13)
library(tidyverse)
library(ggrepel)
```
Look at Flights Data & Structure
```{r}
?flights
str(flights)
head(flights)
```
1. f I am leaving before noon, which two airlines do you recommend at each airport (JFK, LGA, EWR) that will havethe lowest delay time at the 75th percentile?

Filter the dataset so that the new data only has EWR
```{r}
EWRdata <- filter(flights, origin == "EWR")
head(EWRdata)
```
Create a Graph
```{r}
EWRplot <- ggplot(data = EWRdata, mapping = aes(x = carrier, y = arr_delay, size = arr_delay, color = carrier)) +
  geom_point()+
  labs(x = "Carriers",
       y = "Arrival Delay",
       title = "Which two airlines have the lowest arrival delay in EWK airport?",
       subtitle = "Skywest Arilines INc. & Alaska Airlines Inc. have the lowest arrival delay") +
  theme_bw()

EWRplot
```
Filter the dataset so that the new data only has JFK
```{r}
JFKdata <- filter(flights, origin == "JFK")
head(JFKdata)
```
Create a Graph
```{r}
JFKplot <- ggplot(data = JFKdata, mapping = aes(x = carrier, y = arr_delay, size = arr_delay, color = carrier)) +
  geom_point() +
  labs(x = "Carriers",
       y = "Arrival Delay",
       title = "Whuich two airlines have the lowest Arrival Delay in JFK airport?",
       subtitle = "Hawaiian Arilines Inc. & US Airways Inc. have the lowest arrival delay") +
  theme_bw()

JFKplot
```
Filter the dataset so that the new data only has LGA
```{r}
LGAdata <- filter(flights, origin == "LGA")
head(LGAdata)
```
Create a Graph
```{r}
LGAplot <- ggplot(data = LGAdata, mapping = aes(x = carrier, y = arr_delay, size = arr_delay, color = carrier)) +
  geom_point() +
  labs(x = "Carriers",
       y = "Arrival Delays",
       title = "Which two airlines have the lowest Arrival Delay in LGA airport?",
       subtitle = "Skyest Airlines Inc. & Endeavor Air Inc. have the lowest arrival delay") +
  theme_bw()

LGAplot
```

Which destination airport is the worst airport for 
arrival time?
```{r}
WorstAirline <- ggplot(data = flights, mapping = aes(x = origin, y = arr_delay, color = origin, size = arr_delay)) +
  geom_point() +
  labs(x = "Origin Airport", 
       y = "Arrival Delay",
       title = "Which destination airport is the worst airport for arrival time?",
       subtitle = "JFK is the worst location to fly out of",
       caption = "We know this because it has a high density of points") +
  theme_bw()
WorstAirline
```
The worst airline is JFK because, and I was able to figure that out because it has the most points laying towards the top of the graph, meaning it has the most late arrivals. 
